PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed file path to respiratory data

#Read in respiratory data
```{r coping resp cols}
coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/respiratory_coping_glad.rds"))
dim(coping.glad.respiratory.raw)
colnames(coping.glad.respiratory.raw)
```

@@

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING

```{r create numeric sex variable with male=1}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        1,
        0
      )
  )
```

>>>>

#Read in respiratory data
```{r coping resp cols}
coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
dim(coping.glad.respiratory.raw)
colnames(coping.glad.respiratory.raw)
```

@@

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING
The COVID prediction model has coded the sexes opposite to our data set
```{r create numeric sex variable with male=1}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        true = 1,
        false = 0
      )
  )
```
